Chatbots and messaging platforms in the classroom: an analysis from the teacher's perspective

### 2021-11-05 edubots_surveys.Rnw
They are the baseline....

%Why messaging apps are relevant here --> connect to the development of chatbots
Group messaging apps have become a powerful tool to communicate with students. Also, they are the baseline platform for the development of 
chatbots to help with the learning process. After an initial analysis to the answers to the first survey, we realized that there were some prior issues mainly related to the adoption of a technology, chatbots, that generally piggybacks on another, messaging applications. In a technology adoption model, perceived ease of use and perceived usefulness are essential. But it is going to be very difficult for teachers to find {\em chatbots} easy to use if they, previously, do not consider, or simply use, the messaging tools to which they are attached.

>>>>

%Why messaging apps are relevant here --> connect to the development of chatbots
Group messaging apps have become a powerful tool for keeping touch with students. Also, many of them have built-in chatbots 
to enhance the learning process. After an initial analysis to the answers to the first survey, 
we realized that there were some prior issues mainly related to the adoption of a technology, chatbots, that generally 
piggybacks on another, messaging applications. In a technology adoption model, perceived ease of use and perceived usefulness are essential. But it is going to be very difficult for teachers to find {\em chatbots} easy to use if they, previously, do not consider, or simply use, the messaging tools to which they are attached.
